---
title: "How Close is Too Close?"
author: "User Input Location, Displaying Proximity To Agriculture Burns"
output: html_document
---

```{r warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(tmap)
library(rosm)
library(sf)
library(leaflet)
library(leaflet.extras)
library(htmltools)
library(ggmap)
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
ExcelwPDF_Final <- read_csv("C:/Users/bcruiz/OneDrive - University of Southern California/ImperialBurning/Data/ExcelwPDF_Final.csv")%>%
  filter(Acres != 710)

# stats::quantile(ExcelwPDF_Final$Acres, probs = seq(0, 1, 0.25))

AgBurn_sf <- st_as_sf(ExcelwPDF_Final, coords = c("LON", "LATI"), crs = 4326,
         remove = FALSE)

AgBurn_sf <- AgBurn_sf%>%
  mutate(AcreageCat = case_when(Acres < 36 ~ "1-36",
                                Acres < 69 ~ "37-69",
                                Acres < 79 ~ "70-79",
                                Acres < 246 ~ "80 - 245"))
```

```{r warning=FALSE, message=FALSE, echo=FALSE, fig.width=10, fig.height=8}
agburn_elem <- tm_shape(AgBurn_sf)+
  tm_dots(col = "red", alpha = 0.4, id = "", size = "Acres",
          popup.vars = c("Acres: " = "Acres", "Crop: " = "Crop", "Date: " = "Date"))
  # tm_bubbles(col = "AcreageCat", alpha = 0.4, id = "Acres")

# tmap_mode("view")
# 
# tmap_options(basemaps = c("Esri.WorldTopoMap", "Stamen.TonerLite", #<<
#                           "CartoDB.DarkMatter", "OpenStreetMap.Mapnik"),
#              check.and.fix = TRUE)
# agburn_elem%>%  
#   tmap_leaflet() %>%
#   addProviderTiles("Stamen.Toner") %>% 
#   leaflet.extras::addSearchOSM(options = searchOptions(collapsed = FALSE))

pal <- colorNumeric(palette = "OrRd", domain = c(1, 245), reverse = FALSE)

AgBurn_sf%>%
    leaflet()%>%
    addProviderTiles(provider = "OpenStreetMap.Mapnik")%>%
    addProviderTiles("Stamen.TonerHybrid")%>%
    addCircleMarkers(radius = ~sqrt(Acres), color = ~pal(Acres),
                     label = ~paste0("Acres: ", Acres),
                     opacity = 0.7)%>%
    addLegend(title = "Acreage Burned", pal = pal, values = c(1:245),
              position = "topright", opacity = 0.8)%>%
    addSearchOSM(options = searchOptions(collapsed = FALSE))%>%
    addMeasure(position = 'bottomleft',
               primaryLengthUnit = 'miles',
               primaryAreaUnit = 'sqmiles',
               activeColor = '#3D535D',
               completedColor = '#7D4479',
               localization = 'en')
```

<br>

Explore with the different map tiles and enter any address in the search bar to see the proximity to each agriculture burn. Each agriculture burn is scaled to acreage, the larger the colored marker the bigger the burn with legend at the side to describe intensity. **Hovering** on the burns will reveal information about *acreage*. The **measure** tool at the bottom left will measure the distance in miles from one point to another.
